QPLIB: A Library of Quadratic Programming Instances

### 2017-01-23 QPLIB-1.0.tex
make intro part to solution methods independent of set of solvers
fix some latex warnings

\multicolumn{3}{l}{\multirow{1}{\textwidth}{$^{\ddagger}$Applications with many manuscripts cite reviews and recent works. $^{\star}$TSP $\equiv$ Traveling Salesman Problem}} \\ \\ \\

@@

\multirow{1}{.55\textwidth}{{\bf Finance:} Portfolio optimization} & \checkmark & \multirow{1}{.25\textwidth}{\cite{deng-etal:2013,kallrath:2003,lin-etal:2005,maranas-etal:1997,parpas-rustem:2006,rios-sahinidis:2010,FrFG16,FrGe06a,FrGe07a,FrGe09a}} \\ 

@@

\multirow{1}{.55\textwidth}{TSP$^{\star}$ with Neighborhoods} & \checkmark & \cite{gentilini-etal:2013} \\

@@

The structure of this paper is the following. In \S~\ref{sec:QPbasic} we review the basic notions about QP. In particular, \S~\ref{subsec:notation} sets out the notation, \S~\ref{sec:classification} proposes a---to the best of our knowledge, new---taxonomy of QP that helps us in discussing the (very) different classes of QPs, \S~\ref{sec:algo} very briefly reviews the solution methods for QP upon which the solvers we have employed are based, and \S~\ref{subsec:solver} describes the solvers. Then, \S~\ref{sec:lib} describes the process used to obtain the library and its results; the software tools that we have used, and that are freely released together with the library, are discussed in \S~\ref{subsec:tools}. Some conclusions are drawn in \S~\ref{sec:conclusions}, after which in the Appendix a complete description of all the instances of the library is provided.

>>>>

\multicolumn{3}{l}{\multirow{1}{\textwidth}{$^{\ddagger}$Applications with many manuscripts cite reviews and recent works.}} \\ \\ \\

@@

{\bf Finance} \\
Portfolio optimization & \checkmark & \multirow{1}{.25\textwidth}{\cite{deng-etal:2013,kallrath:2003,lin-etal:2005,maranas-etal:1997,parpas-rustem:2006,rios-sahinidis:2010,FrFG16,FrGe06a,FrGe07a,FrGe09a}} \\ \\

@@

\multirow{1}{.55\textwidth}{Traveling Salesman Problem with Neighborhoods} & \checkmark & \cite{gentilini-etal:2013} \\ \\

@@

The structure of this paper is the following. \todo{citation of sections should be uniform: ``\S'' vs. ``Sect.'' vs. ``Section''}In \S~\ref{sec:QPbasic} we review the basic notions about QP. In particular, \S~\ref{subsec:notation} sets out the notation, \S~\ref{sec:classification} proposes a---to the best of our knowledge, new---taxonomy of QP that helps us in discussing the (very) different classes of QPs, \S~\ref{sec:algo} very briefly reviews the solution methods for QP upon which the solvers we have employed are based, and \S~\ref{subsec:solver} describes the solvers. Then, \S~\ref{sec:lib} describes the process used to obtain the library and its results; the software tools that we have used, and that are freely released together with the library, are discussed in \S~\ref{subsec:tools}. Some conclusions are drawn in \S~\ref{sec:conclusions}, after which in the Appendix a complete description of all the instances of the library is provided.
